### 2023-12-21 sections/1-introduction.tex
added related-works subsection in intro

Recent search algorithms to tackling the exponential growth of data include locality-sensitive hashing~\cite{indyk1999sublinear} such as MRPT~\cite{hyvonen2016fast}, hierarchical navigable small world (HNSW) networks~\cite{Malkov2016EfficientAR}, Inverted File indexing~\cite{johnson2019billion}, and entropy-scaling search~\cite{yu2015entropy, ishaq2019clustered}.

TODO: Paragraph summarizing LSH.

@@

@@

>>>>

\subsection{Related Works}
\label{subsec:intoduction:related-works}

Recent search algorithms to tackling the exponential growth of data include hierarchical navigable small world networks (HNSW)~\cite{Malkov2016EfficientAR}, Inverted File indexing (FAISS-IVF)~\cite{johnson2019billion}, random projection and tree building (ANNOY)~\cite{annoy}, and entropy-scaling search~\cite{yu2015entropy, ishaq2019clustered}.

\subsubsection{HNSW}
\label{subsubsec:introduction:related-works:hnsw}

@@

\subsubsection{FAISS-IVF}
\label{subsubsec:introduction:related-works:faiss-ivf}

@@

\subsubsection{ANNOY}
\label{subsubsec:introduction:related-works:annoy}

TODO: Paragraph summarizing ANNOY.

\subsubsection{Entropy-Scaling Search}
\label{subsubsec:introduction:related-works:entropy-scaling-search}
